Review of Group 8 by Group 1

### 2015-02-10 rmtw/a3/latex8.tex
Adding my changes to the document

​\Section{Introduction}
*5 references must be used to support claims in Introduction
Use parts of Abstract and Intro from CM. 
\SubSection{Problem Statement}
Take this from CM. 
How do large companies implement changes in environments which are split by two programming paradigms?

@@

>>>>

%Deficiencies introduction model

​\Section{Introduction}
*5 references must be used to support claims in Introduction
Use parts of Abstract and Intro from CM.

Coping with change in the software development domain is difficult at best, this is further exasperated by trying to apply changes that do not mesh well with existing development paradigms. How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?

\SubSection{Problem Statement}
The purpose of this paper is therefore to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.

%Maybe not this bit-----------------------------------------------------------
To explore this area, we focus on process and design practices that have been introduced at Ericsson EPG.
%Maybe not this bit-----------------------------------------------------------

@@

Little existing literature.
There are gaps: see: nothing about applying changes to two different paradigms at the same time.

\SubSection{Deficiencies in Literature}
What is missing
